%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Surya}{ Prakash}
       {Embedded Systems \& IoT Developer|Pre-final Year B.Tech. Student}

% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    Surya Prakash
    Dept. of Electronics \& Communication Engg.
    The LNMIIT
    Jaipur
    India
    ~
    \href{mailto:suryabvsp@gmail.com}{suryabvsp@gmail.com}
    \href{https://github.com/suryabvsp/}{Github://suryabvsp}
    \href{https://www.linkedin.com/in/suryabvsp/}{LinkedIn://in/suryabvsp}
    ~
  \section{Programming Languages}
    {\color{red} $\varheartsuit$} Embedded C,
    MATLAB,VHDL
    Assembly, \TeX
  \section{Hardware}
    Arduino, RaspberryPi,
    TIVA Launchpad,
    PIC16F MCU
  \section{Softwares}
    Processing, Proteus,
    Keil, Arduino IDE,
    MikroC, Code Composer Studio
  \section{Online Courses}
    IoT Specialisation
    |Coursera(Certified)
    Real Time Bluetooth Networks|EdX
    (Ongoing) 
    ~
    ~
    ~
    ~
    ~
    ~
    \section{Activities}
    Quizzing, Hackathons,
    Tech Fest, MUNs,
    Entrepreneurship Cell
\end{aside}

\section{Interests}

Seeking an opportunity to work on building Smart Devices. Loves programming machines, hence working in embedded systems.\\ Currently working on Real Time Operating Systems, Bluetooth Low Energy and devices for Smart Power Grids. Also an avid Linux enthusiast.

\section{Education}

\begin{entrylist}
   \entry
    {2014–Present}
    {B.Tech.}
    {The LNM Institute of Information Technology | Jaipur}
    {Electronics \& Communication Engineering\\Relevant Courses: Microprocessors, Embedded Systems, Internet of Things.\\CGPA: 7.02}
  \entry
    {2013}
    {Board of Intermediate Education A.P.}
    {Vidyadham Junior College | Hyderabad}
    {Higher Secondary Education | Percentage: 85.66\%}
  \entry
    {2011}
    {CBSE AISSE}
    {Kendriya Vidyalaya 1 | Bhubaneswar}
    {Secondary Education | CGPA: 10/10}
\end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {Jan '17}
    {Hospital Equipment Consultancy}
    {Winter Internship}
    {\emph{Gesture driven Operation Theatre Lights} using PIC16F882 Microcontroller.\\Worked on \textit{MikroC} and \textit{Proteus}. Supervisor: \href{http://lnmiit.ac.in/Department/ECE/ece_FacultyProfile.aspx?nDeptID=119}{Dr. Abhishek Sharma}.}
  \entry
    {Jun-July ’16}
    {LNMIIT Undergraduate Summer Internship Programme}
    {Summer Internship.}
    {\emph{Developing TI RTOS applications and custom BLE profiles on TI CC2650 Sensortag}. Supervisor: \href{http://www.lnmiit.ac.in/Department/ECE/ece_FacultyProfile.aspx?nDeptID=189}{Dr. Santosh Shah}.}
\end{entrylist}

\section{Key Projects}

\begin{itemize}
    \item Non-Intrusive Load Monitoring in Smart Grids [Ongoing]\\
    {\small To Implement NILM algorithms for load desegregation. Mentor: \href{http://www.lnmiit.ac.in/Department/CSE/Department_FacultyProfile.aspx?nDeptID=20296}{Dr. Kumar Padmanabh}.}
    \item Personal Fitness Device [Ongoing]\\
    {\small A BLE personal fitness device working on RTOS. Hardware used: TI MSP 432 launchpad, TI MK-II BoosterPack and TI CC2650 launchpad.}
    \item Object Detection using SONAR based systems\\
    {\small Worked with Arduino and Processing on building an object detection system. Refined the algorithm for better results. Supervisor: \href{http://www.lnmiit.ac.in/Department/ECE/ece_FacultyProfile.aspx?nDeptID=20269}{Dr. M. V. Deepak Nair}. \href{https://github.com/suryabvsp/sonar-project}{[Github]} \href{https://github.com/suryabvsp/sonar-project/blob/master/Sonar%20Project%20Report.pdf}{[Report]}}
\end{itemize}
\textbf{Other Projects}\\
    {\small Sight - Visual Assistance Belt for the Blind [2nd position at LNMHacks(Hackathon) out of 45 teams]\\
    Literature Survey on Ultra Low Power Microcontrollers for Mote Development\\
    Arduino - Autonomous RC Car, Smart Window Screen.\\Circuit Modelling using MATLAB}
\section{References}
\href{http://lnmiit.ac.in/Department/ECE/ece_FacultyProfile.aspx?nDeptID=119}{Dr. Abhishek Sharma} \qquad \href{http://www.lnmiit.ac.in/Department/ECE/ece_FacultyProfile.aspx?nDeptID=20269}{Dr. M. V. Deepak Nair} \qquad \href{http://www.lnmiit.ac.in/Department/ECE/ece_FacultyProfile.aspx?nDeptID=189}{Dr. Santosh Shah}
%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
